\documentclass{article}
\begin{document}
\section{LITEREATURE REVIEW}
\paragraph{This chapter reviews a fast numerical solver for multiphase flows and other algorithms. In this algorithm, finite volume discretization and time stepping algorithms are used to construct a fast and efficient numerical solver.}
\subsection{Existing algorithims}

\paragraph{
The following are the algorithms which are currently being used to solve multiphase flows.}

\paragraph{MfsolverC++. It allows developers to reduce the time spent on the programming, debugging and it makes all implementation aspects cleaner and simpler.}
\paragraph{Global Pressure Model for Isothermal Two-Phase Immiscible Flow. It has two equations for mass conservation in each phase.}
\subsection{Weaknesses of the existing algorithms}
\paragraph{There is time consuming in computation of the results.}
\paragraph{There is also large number of strongly coupled  nonlinear  differential equations in the system which are difficult to read.}
\subsection{The fast numerical solver will use the following methods.}

\paragraph{Finite volume discretization: it’s a method for representing and evaluating partial differential equations in form of algebraic equations. It is easily formulated to allow for un structured meshes.}
\paragraph{Time-stepping algorithm: Here the convergence methods based on the convergence properties of the underlying iterative methods are discussed, and an accurate performance model from which the speedup and other quantities can be estimated is presented.}
\paragraph{Dimensional splitting is an effective method for solving multidimensional problems  in multiphase flows by constructing he integration algorithm from one-dimensional sub-problems to one  dimension at a time.it has been proved that dimensional splitting encounters several limitations when applied for solving conservation laws.}
\paragraph{Local characteristic decomposition is used for accurate resolution of complicated structure of solutions. I t increases the computational costs and controls spurious oscillations when order of accuracy is high.}




\end{document}